Equalizer\\Programming and User Guide

### 2013-01-19 Developer/ProgrammingGuide/paper.tex

\begin{description}
\item[--eq-client] is used to start render client processes. Starts a resident
  render client when used without additional arguments, as described in
  \sref{sResident}. The server appends an undocumented argument to this option
  which is used by the \textsf{eq::Client} to connect to the server and identify
  itself.
\item[--eq-config \textless sessionName\textbar filename.eqc\textgreater] is
  used to configure an application-local server, as described in
  \sref{sGPUSDUsage}.
\item[--eq-layout \textless layoutName\textgreater] activates all layouts of the
  given name on all respective canvases during initialization. This option may
  be used multiple times.
\item[--eq-listen \textless connection\textgreater] configures the
  local node to listen on the given connections. The formation of the connection
  argument is documented in
  \textsf{co::Con\-nec\-tionDescription::fromString()}. This option may be used
  multiple times.
\item[--eq-logfile \textless filename\textgreater] redirects all Equalizer
  output to the given file.
\item[--eq-render-client \textless filename\textgreater] provides an alternate
  executable name for starting render clients. This option is useful if the
  client machines use a different directory layout from the application machine.
\item[--eq-server \textless connection\textgreater] provides a connection
  description when using a separate server process.
\end{description}

>>>>

\begin{description}
\item[--eq-help] shows all available library command line options and their
  usage.
\item[--eq-client] is used to start render client processes. Starts a resident
  render client when used without additional arguments, as described in
  \sref{sResident}. The server appends an undocumented argument to this option
  which is used by the \textsf{eq::Client} to connect to the server and identify
  itself.
\item[--eq-layout \textless layoutName\textgreater] activates all layouts of the
  given name on all respective canvases during initialization. This option may
  be used multiple times.
\item[--eq-modelunit \textless unitValue\textgreater] is used for scaling the
  rendered models in all views. The model unit defines the size of the model wrt
  the virtual room unit which is always in meter. The default unit is 1 (1 meter
  or EQ\_M).
\item[--eq-logfile \textless filename\textgreater] redirects all Equalizer
  output to the given file.
\item[--eq-server \textless connection\textgreater] provides a connection
  description when using a separate server process.
\item[--eq-config \textless sessionName\textbar filename.eqc\textgreater] is
  used to configure an application-local server, as described in
  \sref{sGPUSDUsage}.
\item[--eq-config-flags \textless multiprocess\textbar multiprocess\_db\textbar
  ethernet\textbar infiniband\textbar 2D\_horizontal\textbar
  2D\_vertical\textbar 2D\_tiles\textgreater] is used as input for the
  autoconfiguration to tweak the configuration generation.
\item[--eq-config-prefixes \textless CIDR-prefixes\textgreater] is used as input
  for the autoconfiguration to filter network interfaces.
\item[--eq-render-client \textless filename\textgreater] provides an alternate
  executable name for starting render clients. This option is useful if the
  client machines use a different directory layout from the application machine.
\item[--eq-listen \textless connection\textgreater] configures the
  local node to listen on the given connections. The formation of the connection
  argument is documented in
  \textsf{co::Con\-nec\-tionDescription::fromString()}. This option may be used
  multiple times.

\end{description}
